HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-02 paper/main.tex
Final touches to 4.3

\begin{figure}[t]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{c}
\subfloat[English-German]{
  \iaafig{de}
}
\\
\subfloat[English-Romanian]{
  \iaafig{ro}
}
\end{tabular}
\caption{Plots of HUME scores vs Direct Assesment scores which have been standardised for each crowdsourcing annotator and averaged for 10 annotators. HUME scores are averaged where there were two annotations. 
%The regression is calculated using linear least squares.
}
\label{fig:dacorrelation}
\end{figure}
Recent research~\cite{graham2015accurate,graham2015crowd} has proposed a new approach for collecting 
accuracy ratings. By crowdsourcing a large number of adequacy judgements for each candidate 
translation on a fine-grained 
scale of 0 to 100, we can apply statistical measures which result in reliable aggregate scores. 
It has been shown that mean  judgements correlate very strongly with each other. 
We followed~\citep{graham2015accurate} and collected up to 15 adequacy judgements on most of the
HUME annotated translations for German and Romanian. To ensure high quality judgments
we restricted the IP of the annotators to those of the relevant country. We found that there were too
few Czech and Polish annotators, and removing the IP restriction led to very poor quality results. 
We also removed unreliable crowdsourcing annotators
according to the method discussed in ~\cite{TODO}.

We can see in Figure~\ref{fig:dacorrelation} that HUME and Direct Assesment scores do correlate. 
The Pearsons correlation for en-de is 0.58 and for en-ro is 0.70 which confirms that 
the HUME metric is consistent with previously published methods in human evaluation, even though these
two approaches are very different in their conception.
We argue that although annotating HUME requires more expertise and effort than direct assesment it has
two advantages. It returns fine-grained information about the translations and it can use one 
expert annotator. Direct assesment returns only one aggregate score, and requires a large number
of crowdsourcing workers who may not be available or reliable.

\begin{figure}[t]
\includegraphics[width=0.45\textwidth]{humevsDAcorrtypes-10en-dero.pdf}
\caption{Pearsons correlation HUME scores vs DA for different node types. Struct is correlation for all structural nodes, P+S is correlation for all process and state nodes, H are parallel scene nodes, A participant, C centre, E elaborators, and L linker nodes.}
\label{fig:dacorrelationtypes}
\end{figure}

In Figure~\ref{fig:dacorrelationtypes} we can see an analysis of HUME correlations with DA by HUME node type. Generally correlations are good. Some types of nodes seem to predict the DA scores better than others. The HUME scores on parallel scene nodes (H) and participant nodes (A) seem to correlate more strongly with DA than scores on process and state nodes (P+S) or linker nodes (L).

>>>>

\begin{figure}[t]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{c}
\subfloat[English-German]{
  \iaafig{de}
}
\\
\subfloat[English-Romanian]{
  \iaafig{ro}
}
\end{tabular}
\caption{HUME vs DA scores. DA score have been standardised for each crowdsourcing annotator and averaged across exactly 10 annotators. HUME scores are averaged where there were two annotations. 
%The regression is calculated using linear least squares.
}
\label{fig:dacorrelation}
\end{figure}
Recent research~\cite{graham2015accurate,graham2015crowd} has proposed a new approach for collecting 
accuracy ratings, direct assessment (DA). By crowdsourcing a large number of adequacy judgements for each candidate 
translation on a fine-grained 
scale of 0 to 100, we can apply statistical measures which result in reliable aggregate scores. 
It has been shown that mean DA judgements correlate very strongly with each other. 
We followed~\parcite{graham2015accurate} and collected up to 15 adequacy judgements on most of the
HUME annotated translations for German and Romanian. To ensure high quality judgments
we restricted the IP of the annotators to those of the relevant country. We found that there were too
few Czech and Polish annotators, and removing the IP restriction led to very poor quality results.

We can see in Figure~\ref{fig:dacorrelation} that HUME and Direct Assesment scores correlate reasonably well.  
The Pearsons correlation for en-de is 0.58 and for en-ro is 0.70 overall which confirms that 
the HUME metric is consistent with an accepted human evaluation method, namely DA, 
even though the two metrics are very different in their conception. 
Although DA is a valuable tool for translation research, HUME has two advantages:
it returns fine-grained semantic information about the quality of translations and it only requires one 
annotator. Direct assesment returns a single score, and it needs a large 
crowd which may not be available or reliable.

\begin{figure}[t]
\includegraphics[width=0.45\textwidth]{humevsDAcorrtypes-10en-dero.pdf}
\caption{Pearsons correlation HUME scores vs DA for different node types. Struct refers to all structural nodes, P+S are all process and state nodes, H parallel scene nodes, A participant, C centre, E elaborators, and L linker nodes.}
\label{fig:dacorrelationtypes}
\end{figure}

In Figure~\ref{fig:dacorrelationtypes} we can see an analysis of HUME correlations with DA by HUME node type. We can see that correlation increases when combining different sematic node types and that correlation is highest for node type ``all''. Some types of nodes seem to predict the DA scores better than others. The HUME scores on parallel scene nodes (H) and participant nodes (A) seem to correlate more strongly with DA than scores on process and state nodes (P+S) or linker nodes (L). Center nodes (C) are also more correlated than elaborator nodes (E), which is what we would expect given that center nodes are by definition more important to the semantics of a sentence than elaborators.
